Generating a README.txt file for the Dryad submission of data from study "DateLife: leveraging databases and analytical tools to reveal the dated Tree of Life

### 2022-07-18 dryad/README.Rmd
newick files of fringillidae topologies

file.copy(from = "../tables/table-fringillidae-small-example.csv",
          to = "../dryad/Sanchez-Reyes_etal_2022_table_1.csv",
          overwrite = TRUE)
file.copy(from = "../tables/table-fringillidae-small-example-summary.csv",
          to = "../dryad/Sanchez-Reyes_etal_2022_table_2.csv",
          overwrite = TRUE)
file.copy(from = "../tables/table-fringillidae-all-congruified.csv",
          to = "../dryad/Sanchez-Reyes_etal_2022_supplementary_table_S1.csv",
          overwrite = TRUE)
file.copy(from = "../tables/table-fringillidae-all-congruified.pdf",
          to = "../dryad/Sanchez-Reyes_etal_2022_supplementary_table_S1.pdf",
          overwrite = TRUE)
file.copy(from = "../tables/table-fringillidae-all-summary.csv",
          to = "../dryad/Sanchez-Reyes_etal_2022_supplementary_table_S2.csv",
          overwrite = TRUE)
file.copy(from = ".../tables/table-fringillidae-all-summary.pdf",
          to = "../dryad/anchez-Reyes_etal_2022_supplementary_table_S2.pdf",
          overwrite = TRUE)
file.copy(from = "../figures/figure-workflow/median_chronogram.tre",
          to = "../dryad/Sanchez-Reyes_etal_2022_figure_1_chronogram_mock_example.tre")
```

>>>>

file.copy(from = "../tables/table-fringillidae-small-example.csv",
          to = "../dryad/Sanchez-Reyes_etal_2022_table_1.csv",
          overwrite = TRUE)
file.copy(from = "../tables/table-fringillidae-small-example-summary.csv",
          to = "../dryad/Sanchez-Reyes_etal_2022_table_2.csv",
          overwrite = TRUE)
file.copy(from = "../tables/table-fringillidae-all-congruified.csv",
          to = "../dryad/Sanchez-Reyes_etal_2022_supplementary_table_S1.csv",
          overwrite = TRUE)
file.copy(from = "../tables/table-fringillidae-all-congruified.pdf",
          to = "../dryad/Sanchez-Reyes_etal_2022_supplementary_table_S1.pdf",
          overwrite = TRUE)
file.copy(from = "../tables/table-fringillidae-all-summary.csv",
          to = "../dryad/Sanchez-Reyes_etal_2022_supplementary_table_S2.csv",
          overwrite = TRUE)
file.copy(from = ".../tables/table-fringillidae-all-summary.pdf",
          to = "../dryad/anchez-Reyes_etal_2022_supplementary_table_S2.pdf",
          overwrite = TRUE)
file.copy(from = "../figures/figure-workflow/median_chronogram.tre",
          to = "../dryad/Sanchez-Reyes_etal_2022_figure_1_chronogram_mock_example.tre",
          overwrite = TRUE)
file.copy(from = "../figures/figure-small-example/median_chronogram.tre",
          to = "../dryad/Sanchez-Reyes_etal_2022_figure_3_chronogram_small_example.tre",
          overwrite = TRUE)
file.copy(from = "../figures/figure-fringillidae/median_chronogram.tre",
          to = "../dryad/Sanchez-Reyes_etal_2022_figure_5_chronogram_finches_example.tre",
          overwrite = TRUE)
file.copy(from = "../figures/fringillidae-topologies/fringillidae_monophyletic_topology.tre",
          to = "../dryad/Sanchez-Reyes_etal_2022_figure_4A_topology_finches_mrca.tre",
          overwrite = TRUE)
file.copy(from = "../figures/fringillidae-topologies/fringillidae_paraphyletic_topology.tre",
          to = "../dryad/Sanchez-Reyes_etal_2022_figure_4B_topology_finches_ncbi.tre",
          overwrite = TRUE)
```
